\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\name{KANAGARAJ}{M}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}
\begin{document}
\makecvtitle
\vspace*{-16mm}
\begin{center}
    
\end{center}
\begin{center}
\begin{tabular}{ c c c }
\faMobile\enspace +91 6383588281 & \enspace\faGoogle\enspace  kanagarajm638@gmail.com \enspace\faHome\enspace Coimbatore, TN\\
\faLinkedin\enspace \color{blue} \href{https://www.linkedin.com/in/kanagaraj-m-b86439227/}{kanagaraj-m-b86439227} &
\faGithub\enspace \color{blue} \href{https://github.com/KANAGARAJ-M}{KANAGARAJ-M} & \faGlobe \enspace \color{blue} \href{https://kanagaraj.nocorps.org/}{Portfolio}\end{tabular}
\end{center}

\section{Profile}
{Aspiring Full-Stack Developer with hands-on experience in Flutter, Dart, and modern web frameworks like React.js and Vue.js. Proven ability to develop user-centric applications with seamless functionality and appealing UI. Adept at leveraging Firebase for real-time data management and authentication. Eager to contribute technical expertise and creative problem-solving skills to dynamic, growth-oriented teams.}


\section*{Skills}
\begin{itemize}[leftmargin=0.15in, label={ •}]
  \item \textbf{Programming Languages :} Java, Dart, JS
  \item \textbf{Frameworks :} Flutter, React.js
  \item \textbf{Web Technologies :} HTML, CSS
  \item \textbf{Database \& Cloud :} Firebase Auth, Firebase Storage, Firebase Firestore, ISAR DB, SQL
  \item \textbf{Tools \& Platforms : }Android Studio, Git, API, Riverpod
  % \item \textbf{Tools :} Git, GitHub, Android Studio
  \item \textbf{Soft Skills :} Leadership, Team Work, Quick learner, Problem Solving
\end{itemize}


% \section{Areas of Expertise} 
% {Full Stack Web Developer - Angular Js - React Js - Software Development - Flutter Cross Platform Application Developer - Software Testing - UI/UX}

\section{Projects}

\customcventry{
}{{\color{blue}\href{https://github.com/KANAGARAJ-M}{(Github)}}}{Addagram – Social Media Platform}{}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Comprehensive social media platform built with Flutter, Dart, Firebase, and Python backend.
\item Features real-time messaging, photo/video sharing, user profiles, and social interactions.
\item Implemented secure authentication, cloud storage, and real-time database synchronization.
\item Optimized for cross-platform deployment with responsive UI/UX design.
\end{itemize}}}

\customcventry{
}{{\color{blue}\href{https://github.com/KANAGARAJ-M}{(Github)}}}{Kodex E-Learning Platform}{}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Interactive e-learning platform with course management, video streaming, and progress tracking.
\item Built using Flutter, Firebase, with integrated video streaming and analytics capabilities.
\item Features include course management, video lectures, progress tracking, and interactive quizzes.
\item Designed for both students and educators with comprehensive learning management tools.
\end{itemize}}}

\customcventry{
}{{\color{blue}\href{https://github.com/KANAGARAJ-M}{(Github)}}}{Warehouse Management System}{}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Complete enterprise warehouse management system with inventory tracking and order processing.
\item Developed using React, Python, PostgreSQL, and REST APIs for scalable backend architecture.
\item Features inventory tracking, order management, automated reports, and real-time analytics.
\item Implemented automated reporting system and real-time data visualization dashboard.
\end{itemize}}}

\customcventry{
}{{\color{blue}\href{https://github.com/KANAGARAJ-M}{(Github)}}}{Poultry Management System}{}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Digital solution for poultry farm management including livestock tracking and health monitoring.
\item Built with Flutter, Firebase, IoT Integration, and Analytics for comprehensive farm management.
\item Features livestock tracking, health monitoring, production analytics, and feed management.
\item Integrated IoT sensors for real-time monitoring and automated data collection.
\end{itemize}}}

\customcventry{
}{{\color{blue}\href{https://github.com/KANAGARAJ-M}{(Github)}}}{PDF Tools Suite}{}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Comprehensive PDF manipulation tools including merge, split, convert, and editing capabilities.
\item Developed using React, JavaScript, PDF.js, and Web APIs for client-side processing.
\item Features PDF merge/split, format conversion, text extraction, and document editing.
\item Optimized for web deployment with responsive design and offline functionality.
\end{itemize}}}

\customcventry{
}{{\color{blue}\href{https://github.com/KANAGARAJ-M}{(Github)}}}{Blue Dev Connect – Developer Network}{}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Professional networking platform connecting developers with project collaboration features.
\item Built using React, Node.js, MongoDB, and Socket.io for real-time communication.
\item Features developer profiles, project collaboration, skill matching, and real-time chat.
\item Implemented advanced search and matching algorithms for developer connections.
\end{itemize}}}




% \section{Internship and Experience}
% \customcventry{Feb - Jun 2024}{{\color{blue}\href{https://marcellotech.com/}{(Marcello Tech)}}}{App Development in Flutter and Android Internship,}{Tamil Nadu,}{}{
% {\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
% \item Completed a two-month internship focusing on mobile app development using Flutter and Android.
% \item Developed and implemented mobile application features under the guidance of senior developers.
% \item Collaborated with a team to troubleshoot and debug application issues, ensuring smooth user experiences.
% \item Participated in code reviews and contributed to enhancing application performance and functionality.
% \item Gained hands-on experience with industry-standard development tools and practices.
% \end{itemize}}}

\section*{Patent Publication}
\begin{itemize}[leftmargin=0.15in, label={ •}]
  \item \textbf{Chat UP Application using Flutter and dart : } Application number(202441047154A)
  
\end{itemize}





\section{Education}
\customcventry{2021-2025}{\color{blue}\href{https://maps.app.goo.gl/1g7YbpsmsTv59AB26}{(V.S.B College of Engineering Technical Campus)}}{B.E Computer Science and Engineering}{Tamil Nadu}{}{}{
% Relevant Courses: C, JAVA, Web Technologies. 
CGPA - 7.9/10
}
% {\item CGPA - 7.8/10}

\customcventry{2020-2021}{\color{blue}\href{https://maps.app.goo.gl/swjMz2NegtAx1KPa7}{(RKR Higher Secondary School)}}{HSC 2nd Year}{Tamil Nadu}{}{}{Percentage - 75.6\%}

\customcventry{2018-2019}{\color{blue}\href{https://maps.app.goo.gl/swjMz2NegtAx1KPa7}{(RKR Higher Secondary School)}}{SSLC}{Tamil Nadu}{}{}{Percentage - 66.4\%}




\section{Online Courses, Internship \& Certifications}
{\begin{itemize}[label=\textbullet]
    \item Mobile App Development with FLUTTER and ANDROID Internship (Feb - Jun 2024) - \underline{\color{blue}\href{https://drive.google.com/file/d/106r6WD5MoSY4W-4qcN8Q6bOjGdFwLJle/view?usp=sharing}{Marcello Tech}}
      \item Android Development Essential Training:  - \underline{\color{blue}\href{https://www.linkedin.com/learning/certificates/3d84c3c470dff3dbd09221f12004410fbdb972d52898465a478ffb237e45b191}{LinkedIn Learning }}
      \item Full Stack Android Development and Mobile App Marketing - \underline{\color{blue}\href{https://www.udemy.com/certificate/UC-9390eed1-94c8-4a98-a2d1-ccac9d444f3b/}{Udemy}}
      \item NM - TNCPL Certificate - \underline{\color{blue}\href{https://drive.google.com/file/d/1dBxFOHJ8DFHbNkEPyetAinCPjiz-FSus/view?usp=sharing}{Guvi}}
      \item Angular - \underline{\color{blue}\href{https://drive.google.com/file/d/1Bws5M4kNewjU-QVsx7zVGm3iZ2hZC0Ea/view?usp=sharing}{Infosys springboard}}
     
       % \item Python Full Stack Internship (Jul. 2023) - \underline{\color{blue}\href{https://drive.google.com/file/d/1bME_ElTKVs88btyjbtSHyujcnBO0H-dL/view?usp=sharing}{Pantech e-learning}} 
  \end{itemize}} 





% \section*{Areas of Expertise}
% \begin{itemize}[leftmargin=0.15in, label={ •}]
%     \item Full Stack Web Development
%     \item AngularJS \& ReactJS
%     \item Flutter Cross-Platform Application Development
%     \item Mobile App Development (Android)
%     \item Software Development \& Testing
%     \item UI/UX Design
%     \item Firebase Authentication \& Storage
%     \item Cloud Firestore
%     \item Version Control with Git \& GitHub
% \end{itemize}



% \newpage




% \section{Languages}
% \begin{multicols}{2}
%     \begin{itemize}[label=\textbullet]
%     \item \textbf{English} [Intermediate]
%     \item {\textbf{Tamil} [Native] }
%     % \item {\textbf{Spanish} [Native]}
%     % \item {\textbf{German} [Basic] - A1}
%     \end{itemize}
% \end{multicols}
\end{document}